Video Understanding : A review of action detection-recognition dataset

### 2024-02-06 conference_101719.tex
AVA + HMDB51

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tabularx,booktabs}
\usepackage[utf8]{vietnam}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Video Understanding : A review of action detection-recognition dataset}

\author{\IEEEauthorblockN{1\textsuperscript{st} Viet Hang Duong}
\IEEEauthorblockA{\textit{Dept of Computer Science} \\
\textit{University of Information Technology}\\
Ho Chi Minh City, Viet Nam \\
hangdv@uit.edu.vn}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Duc Manh Nguyen Dang}
\IEEEauthorblockA{\textit{Dept of Computer Science} \\
\textit{University of Information Technology}\\
Ho Chi Minh City, Viet Nam \\
22520847@gm.uit.edu.vn}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Ngoc Tram Phan Huynh}
\IEEEauthorblockA{\textit{Dept of Computer Science} \\
\textit{University of Information Technology}\\
Ho Chi Minh City, Viet Nam \\
22521500@uit.edu.vn}
}

\maketitle

@@

\begin{IEEEkeywords}
Dataset Overview 
\end{IEEEkeywords}

@@

In the mid-1940s to 1950s, scientists from various fields posed the question of creating an artificial brain, leading to the establishment of the field of Artificial Intelligence (AI) as an academic discipline at the Dartmouth Summer Research Project on Artificial Intelligence in 1956. Since then, numerous studies have been conducted to harness the computational power of computers in addressing problems related to human-level cognition. While notable successes have been achieved, such as Deep Blue defeating reigning world chess champion Garry Kasparov on May 11, 1997, and a team from Carnegie Mellon University winning the DARPA Grand Challenge in 2007 with a self-navigating vehicle covering 55 miles in an urban environment while adhering to traffic safety measures, these accomplishments were primarily based on the application of advanced techniques and the remarkable progress in computer power, rather than revolutionary models. The field of AI has also faced challenges, experiencing two periods of stagnation known as "AI winters": one from 1974 to 1980 and another from 1987 to 1993. During these periods, funding was reduced due to unmet research expectations and limited economic benefits from commercializing AI products. It was not until the era of big data and significant advancements in computer hardware that AI gained increased attention and popularity within the research community. AI competitions began to be organized, particularly in computer vision, attracting numerous research groups. In 2010, the ImageNet Large Scale Visual Recognition Challenge (ILSVRC) \cite{ILSVRC} was initiated, aiming to build upon the success of the PASCAL VOC challenge \cite{PASCALVOC} by evaluating model performance in image recognition tasks.

@@

\begin{figure} [h]
	\centering
	\includegraphics[width=1.\linewidth]{fig_info/fig1/ILSVRCChampionTeamOvertheYears}
	\caption{ILSVRC champion team over years on classification task}
	\label{fig:ilsvrcchampionteamovertheyears}
\end{figure}

@@

The problem of Action Recognition existed before the rise of CNN. Solutions for action recognition during this period often involved feature extraction using various methods to obtain a feature vector from the data, followed by a classifier, typically a Support Vector Machine (SVM). The datasets used were also limited, as shown in Table \ref{config}, which lists prominent datasets from before 2012. It can be observed that in terms of scale (number of classes, number of video clips), the datasets were still quite limited.

\begin{table}[!htbp]
	\centering
	\caption{Action recognition dataset}
	\begin{tabular}{c|c c c c}
		\toprule
		Name & Year & NumClass & Clip/Class & Ref \\
		\midrule
		KTH & 2004 & 6 & 100 & \cite{KTH} \\
		Weizmann & 2005 & 9 & 9 & \cite{Weizmann} \\
		IXMAS & 2007 & 11 & 33 & \cite{IXMAS} \\
		Hollywood & 2008 & 8 & 30-129 & \cite{HollyWood} \\
		UCF Sports & 2008 & 9 & 14-35 & \cite{UCFSports} \\
		Hollywood2 & 2009 & 12 & 61-278 & \cite{Hollywood2} \\
		UCF YouTube & 2009 & 11 & 100 & \cite{UCFYouTube} \\
		Olympic & 2010 & 16 & 50 & \cite{Olympic} \\
		HMDB51 & 2011 & 51 & $\geq$ 100 & \cite{HMDB51} \\
		UCF101 & 2012 & 101 & & \cite{UCF101} \\
		\bottomrule
	\end{tabular}%
	\label{config}
\end{table}%

The CNN model, with its numerous parameters, is prone to overfitting, especially when dealing with small amounts of data. During the explosion of CNN, research groups faced many challenges due to data scarcity. Methods like data augmentation were effective solutions, but it was still necessary to supplement larger and more complex datasets to meet the growing demand for data in CNN models. This would establish a solid foundation for future research. Realizing this need, research groups from all over the AI research community have continuously improved and published increasingly refined datasets. These datasets play a crucial role as a common benchmark for comparing different models.

@@

>>>>

%\documentclass[conference]{IEEEtran}
\documentclass[10pt,onecolumn,letterpaper]{article}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tabularx,booktabs}
\usepackage[utf8]{vietnam}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

	\title{Video Understanding : A review of action detection-recognition dataset}
	%
	%\author{\IEEEauthorblockN{1\textsuperscript{st} Viet Hang Duong}
		%\IEEEauthorblockA{\textit{Dept of Computer Science} \\
			%\textit{University of Information Technology}\\
			%Ho Chi Minh City, Viet Nam \\
			%hangdv@uit.edu.vn}
		%\and
		%\cpvrauthorblockN{2\textsuperscript{nd} Duc Manh Nguyen Dang}
		%\IEEEauthorblockA{\textit{Dept of Computer Science} \\
			%\textit{University of Information Technology}\\
			%Ho Chi Minh City, Viet Nam \\
			%22520847@gm.uit.edu.vn}
		%\and
		%\IEEEauthorblockN{3\textsuperscript{rd} Ngoc Tram Phan Huynh}
		%\IEEEauthorblockA{\textit{Dept of Computer Science} \\
			%\textit{University of Information Technology}\\
			%Ho Chi Minh City, Viet Nam \\
			%22521500@uit.edu.vn}
		%}%

	\author{First Author\\
		{\tt\small firstauthor@i1.org}
		% For a paper whose authors are all at the same institution,
		% omit the following lines up until the closing ``}''.
	% Additional authors and addresses can be added with ``\and'',
	% just like the second author.
	% To save space, use either the email address or home page, not both
	\and
	Second Author\\
	{\tt\small secondauthor@i2.org}
}
\maketitle

@@

@@

Although the field of artificial intelligence emerged in the mid-1990s, it took
several decades for significant progress to be made, thanks to the remarkable
advancements in computer hardware - greater computing power and easier
accessibility. As a result, the research community's interest in AI has
significantly increased. AI competitions began to be organized, particularly in
computer vision, attracting numerous research groups. In 2010, the ImageNet
Large Scale Visual Recognition Challenge (ILSVRC) \cite{ILSVRC} was initiated,
aiming to build upon the success of the PASCAL VOC challenge \cite{PASCALVOC} by
evaluating model performance in image recognition tasks.

@@

\begin{figure} [h]
	\centering

	\includegraphics[width=1.\linewidth]{fig_info/fig1/ILSVRCChampionTeamOvertheYears}
	\caption{ILSVRC champion team over years on classification task}
	\label{fig:ilsvrcchampionteamovertheyears}
\end{figure}

@@

The problem of Action Recognition existed before the rise of CNN. Solutions for
action recognition during this period often involved feature extraction using
various methods to obtain a feature vector from the data, followed by a
classifier, typically a Support Vector Machine (SVM). This approach is called
"hand-crafted feature" and it continued to dominate other methods, including
CNNs, until 2015 because CNN models were still relatively new and not
extensively explored. Over time, the research community gradually replaced these
hand-crafted feature methods with CNNs. Continuous advancements and proposals of
CNN models for action recognition have been made, such as Two-stream networks,
Segment-based methods, Multi-stream networks, 3D CNNs, and so on. Alongside
these developments, there has been an increasing demand for computational power
and a significant growth in the amount of data. The datasets used in this period
were also limited, as shown in Table \ref{config}, which lists prominent
datasets from before 2012. It can be observed that in terms of scale (number of
classes, number of video clips), the datasets were still quite limited.

\begin{table}[h]
	\centering
	%\small
	\caption{Action recognition dataset}
	\begin{tabular}{l|l l l l}
		\toprule
		Name & Year & NumClass & Clip/Class & Ref \\
		\midrule
		KTH & 2004 & 6 & 100 & \cite{KTH} \\
		Weizmann & 2005 & 9 & 9 & \cite{Weizmann} \\
		IXMAS & 2007 & 11 & 33 & \cite{IXMAS} \\
		Hollywood & 2008 & 8 & 30-129 & \cite{HollyWood} \\
		UCF Sports & 2008 & 9 & 14-35 & \cite{UCFSports} \\
		Hollywood2 & 2009 & 12 & 61-278 & \cite{Hollywood2} \\
		UCF YouTube & 2009 & 11 & 100 & \cite{UCFYouTube} \\
		Olympic & 2010 & 16 & 50 & \cite{Olympic} \\
		\bottomrule
	\end{tabular}%
	\label{config}
\end{table}%

Building a dataset typically goes through four steps: (1) Defining a set of
predefined actions, (2) Collecting videos from data sources, (3) Annotating the
data (either automatically, semi-automatically, or manually), (4) Cleaning and
filtering the data to remove duplicates and noise. Each step presents its own
challenges. In step (1), defining an action is not a simple task as humans often
perform complex combinations of gestures. So, what constitutes an "atomic
action"? In step (2), do the video sources comply with copyright rules? Privacy
regulations? Is the dataset stable (not prone to loss or replacement)? In step
(3), the workload scales with the dataset size, and there can be vague
boundaries in determining the start and end of an action. In step (4), what
criteria are used to evaluate whether a video meets the standards for usability?
There are many related questions, such as the availability of human and
financial resources, required to meet the demands of building a comprehensive
research dataset. Furthermore, considering the context before CNNs gained
significant prominence, investing in developing a large-scale dataset was highly
risky.

CNN models possess immense power that scales with their complexity., is prone to
overfitting, especially when dealing with small amounts of data. During the
explosion of CNN, research groups faced many challenges due to data scarcity.
Methods like data augmentation were effective solutions, but it was still
necessary to supplement larger and more complex datasets to meet the growing
demand for data in CNN models. Another reason is that the remarkable success of
CNNs in image processing tasks has been greatly contributed by large-scale
datasets like ImageNet. However, in the video domain, there is currently no
comparable dataset to ImageNet. Realizing this need, research groups from all
over the AI research community have continuously improved and published
increasingly refined datasets. These datasets play a crucial role as a common
benchmark for comparing different models.

\section{Review}

\subsection{HMDB51}

\begin{itemize}
	\item Year : 2011
	\item Paper : HMDB: A Large Video Database for Human Motion Recognition
	\cite{HMDB51}.
\end{itemize}

\subsubsection{\textbf{Context and construction perspective}}
KTH \cite{KTH} and Weizmann \cite{Weizmann} have long been regarded as
pioneering datasets in the early stages of action recognition. However, over
time, their limitations have become evident, particularly in terms of a
restricted number of action categories and simplistic background contexts. With
the advent of recent models, achieving accuracy rates exceeding 90\% became
commonplace. As a result, there is a growing demand for alternative datasets
that present more substantial challenges, aiming to push the boundaries and
enhance the capabilities of action recognition systems. The dataset is carefully
designed to highlight differences among action categories based on motion rather
than static poses. With the valuable contribution, the dataset has a potential
of significantly enhance the evaluation and future utilization of recognition
systems in real life.

\subsubsection{\textbf{Data collection methods}}
A group of student is asked to collect and annotate any segment which represents
a single non-ambiguous human action from videos. The videos are sourced from
digitized movies, public databases like the Prelinger archive, additional online
videos, as well as content from YouTube, Google videos and other videos from
internet. Students also were asked to consider some minimum quality standard : 
only one action per clip, minimum height for main actor should be 60 pixels,
minimum contrast level, minimum of clip length is 1 second, acceptable
compression artifacts, etc.

\subsubsection{\textbf{Data distribution}} 
It includes 6,766 video clips covering 51 different action categories, with each
category having at least 101 clips. 
\begin{itemize}
	\item Train : for each action, 70 random clips are used.
	\item Validation : no validation set.
	\item Test : for each action, 30 random clips are used. 
\end{itemize}

The authors generated three distinct training/testing split follow above rule,
ensure that no test clip also train clip.

\subsubsection{\textbf{Annotations}}

\begin{figure}[h]
	\centering
	\includegraphics[width=1.\linewidth]{"fig_info/fig2/Untitled Diagram.drawio"}
	\caption{}
	\label{fig:untitled-diagram}
\end{figure}

For each class, there will be 3 split files as mentioned above. Each file will
include the names of all the videos in the same class along with an index
belonging to $\lbrace 0, 1, 2 \rbrace$ as shown in Figure
\ref{fig:untitled-diagram}. The file used for training is indexed as 1, for
testing it is 2, and 0 indicates that it is not used in this split.

\begin{table}[h]
	\centering
	\caption{Action recognition dataset}
	\begin{tabular}{l | l     }
		\toprule
		PROPERTY & CATEGORIES \\
		\midrule
		Visible body parts & head(h), upper body(u), full body (f), lower body(l)\\ 
		Camera motion & motion (cm), static (nm) \\
		Number of people involved in the action	& single (np1), two (np2), three
		(np3)\\
		Camera viewpoint & front (fr), back (ba), left(le), right(ri) \\
		Video quality & good (goo), medium (med), ok (bad)	\\

		\bottomrule
	\end{tabular}%
	\label{config2}
\end{table}%

The name of each video also carries a meaning, with a specific structure as
follows: \\
\text{vid-name\_class-name\_vible-body-part\_cam-motion\_num-of-people\_cam-viewpoint\_vid-quality}\\
The abbreviations used are listed in Table \ref{config2}. \\
For example, the name
IPL\_Awards\_Ceremony\_shake\_hands\_f\_cm\_np2\_ba\_med\_0.avi represents a
video titled IPL Awards Ceremony, belonging to the shake hands class, with 'f'
indicating full body, 'cm' indicating motion, 'np2' indicating two people, 'ba'
representing back viewpoint, and 'med' indicating medium quality.

\subsection{AVA}

\begin{itemize}
	\item Year : 2018
	\item Paper : AVA: A Video Dataset of Spatio-temporally Localized Atomic Visual
	Actions \cite{AVA}
\end{itemize}

\subsubsection{\textbf{Context and construction perspective}}

Popular action classification datasets such as KTH \cite{KTH}, Weizmann
\cite{Weizmann}, HMDB51 \cite{HMDB51}, and UCF101 \cite{UCF101} only consist of
short clips manually trimmed to capture a single action. Newer datasets like
Sports-1M \cite{Sports1M}, YouTube-8M \cite{YouTube8M}, Something-something
\cite{somethingsomething}, and Moments in Time \cite{momentsintime} focus on
larger-scale data and are often annotated automatically, leading to noisy
annotations. Some recent studies, such as ActivityNet \cite{ActivityNet}, THUMOS
\cite{THUMOS}, and Charades \cite{Charades}, utilize a large number of videos
containing multiple actions but only provide temporal annotations. Recognizing
the limitations from their perspective, the authors of this paper proposed the
AVA dataset.

\subsubsection{Data collection methods}

The process of constructing the AVA dataset involves five steps : action
vocabulary generation, movie and segment selection, person bounding box
annotation, person linking and action annotation.

\begin{itemize}
	\item \textbf{Action vocabulary generation} : They generate action vocabulary
	base on three principle :  
	\subitem \textit{Generality} : Generic action in daily-life scenes, opposite of
	specific actions in a specific situation, for example, playing football on a
	football field, would be general or nonspecific actions in a general situation.
	\subitem \textit{Atomicity} : Independent of interacted objects (e.g., hold
	without specifying what object to hold).
	\subitem \textit{Exhaustivity} : The authors initialized list of actions using
	knowledge
	from previous datasets. They iterated through this list multiple times until it
	covered approximately 99\% of the actions in the AVA dataset.

	\item \textbf{Movie and segment selection} : Raw video content is sourced from YouTube. The authors initially compile a list of top actors from various nationalities. Each actor is then searched using a YouTube query, retrieving up to 2000 results. The selected videos must fall under the categories of "film" or "television," have a duration of over 30 minutes, be uploaded at least one year prior, and have a minimum of 1000 views. Additionally, black and white videos, low-resolution videos, animated and cartoon content, gaming videos, as well as videos containing adult content, are excluded. Each video is partition into a 15-minute long segment and divided into 897 movie segments. The result is 430 videos.

	\item \textbf{Person bounding box annotation} : First, the bounding boxes are automatically detected using the Faster-RCNN \cite{faster-rcnn} person detector, which significantly reduces the manual annotation time. Then, annotators re-annotate the missed boxes to ensure complete coverage. In the final step, incorrectly labeled boxes are marked and removed.

	\item \textbf{Person link annotation} : The bounding boxes are linked using person embeddings \cite{personembedding}, and then the optimal matching with the Hungarian algorithm \cite{TheHungarian} is applied to match the boxes together. In order to increase accuracy, annotators remove false positive boxes in the next step.

	\item \textbf{Action annotation} : Recognizing the practicality that annotators may make labeling mistakes is unavoidable when dealing with up to 80 classes, the authors divided Action annotation into two stages: action proposal and verification. In the proposal stage, annotators are required to suggest action classes, and these proposals are verified by annotators in the verification stage.

\end{itemize}

\subsubsection{Data distribution}

	In total, there are 430 videos covering 80 classes, with each video contributing 15 minutes at a sample rate of 1Hz (meaning one frame per second, 897 segments per 15 minutes). The train/val/test ratio is divided as 55:15:30, respectively.
	\begin{itemize}
		\item Train : 235 videos, 211k segments.
		\item Val : 64 videos, 57k segments.
		\item Test : 131 videos, 118k segments.
	\end{itemize}

\subsubsection{Annotation}

The AVA action dataset has four versions : v1.0, v2.0, v2.1 and v2.2. There are two key differences between AVA v2.2 and v2.1. Firstly, an additional round of human rating was carried out to include missing labels, resulting in a 2.5\% increase in the total number of annotations. Secondly, box locations were corrected for a few videos that had aspect ratios significantly larger than 16:9. Regarding AVA v2.1, the only modification compared to v2.0 was the removal of a few duplicate movies. The class list and label map remained unchanged from v1.0. The differences between v1.0 and v2.0 is not mentioned by authors.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\linewidth]{"fig_info/fig3/Untitled Diagram.drawio"}
	\caption{}
	\label{fig:untitled-diagram2}
\end{figure}

Figure \ref{fig:untitled-diagram2} lists the annotation files provided across different versions, v2.0 is not mentioned because it has been replaced by v2.1. Unlike v1.0, v2.1, and v2.2 include additional action list files (60 classes as a subset of the 80 classes in AVA), which serve the purpose of the ActivityNet Challenge \cite{ActivityNet}. Additionally, there are included files and excluded files. Raters typically provided annotations at timestamps ranging from 902 to 1798, inclusive, in seconds, with a 1-second interval. Performance evaluation includes all these "included" timestamps, even those where raters indicated the absence of any action. However, for certain videos, specific timestamps were excluded from annotation due to raters flagging the corresponding video clips as inappropriate. Evaluation of performance does not take into account the "excluded" timestamps.\\

The format of a row is the following: video\_id, middle\_frame\_timestamp, person\_box, action\_id, person\_id , as described on the official website :
\begin{itemize}
	\item video\_id: YouTube identifier
	\item middle\_frame\_timestamp: the timestamp in seconds from the start of the YouTube video
	\item person\_box: the bounding box coordinates of the person, given as the top-left $(x_1, y_1)$ and bottom-right $(x_2, y_2)$ points normalized with respect to the frame size. The coordinate range is from $(0.0, 0.0)$ at the top left to $(1.0, 1.0)$ at the bottom right.
	\item action\_id: the identifier of an action class
	\item person\_id: a unique integer that allows linking this box to other boxes depicting the same person in adjacent frames of the video.
\end{itemize}

@@

s
